Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-05-17 sports_analytics.Rmd
soccer refs
WP refs

@@

>>>>

@fernandez2021epvsoccer A framework for the fine-grained evaluation of the instantaneous expected value of soccer possessions

@decroos2019playeraction Actions Speak Louder than Goals: Valuing Player Actions in Soccer

@@

Some refs (cite later)

https://www.degruyter.com/document/doi/10.1515/jqas-2013-0100/html
https://www.taylorfrancis.com/chapters/edit/10.1201/9781315166070-14/situational-success-evaluating-decision-making-football-keith-goldner
http://stat.wharton.upenn.edu/~stjensen/papers/shanejensen.basketball2016.pdf
https://arxiv.org/pdf/2204.11777.pdf
